
\cvsection{SKILLS}
\begin{itemize}
\item\bf{Course Work:}\normalfont{ Operating System, DBMS, 
Computer Networking, Cloud Computing, Project Management .}
\item\bf{Web development}\normalfont{: HTML,Javascript, CSS , Django ,Flask .} 
\item\bf{Networking}\normalfont{: TCP/IP,OSI, SSH, DNS, DHCP, HTTPS , Firewall ,Cyber Attacks }
\item\bf{Testing Tool}\normalfont{: Nmap , Burpsuite ,wireshark}
\item\bf{Tools}\normalfont{: VsCode,Android studio, Conda, Pycharm, Xampp ,Oracle VirtualBox, MySQL ,Linux, Github.}
\item\bf{Extras:}\normalfont{MS Excel,Ms Office,Power Point, Word }
\end{itemize}


\cvsection{Language Proficiency}
\begin{itemize}

\item\bf{Python:} \starRating{5} Expert \\
\item\bf{Java:} \starRating{4} Intermediate \\
\item \bf{C++:} \starRating{3} Basic \\
\item \bf {SQL:}\starRating{4} Intermediate 

\end{itemize}
% \divider
% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

%\cvtag{Hard-working (18/24)} 
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}

% \cvsection{Achievements}
% \begin{itemize}
% \item \bf{5 Star in SQL}  \normalfont at HackerRank
% \item \bf{200+ } \normalfont Problem solved on GFG ,\bf{100+ } on Leetcode
% \item Secured 576 rank in India \bf{GFG HACK-A-THON}
% \item \normalfont Top 10 Performer in \bf{Hackstomp 5.0 | UCOE Hackathon},Thane
% \smallskip
% \item \normalfont Participated in \bf{‘VNPS National level Project showcase 2023’}
% \smallskip

% \end{itemize}

%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}

\cvsection{Projects}
\cvproject{{Movie recommendation using Flask api}}
\begin{itemize}
\item Integrated machine learning models to analyze user data and provide accurate movie suggestions.
\item Applied authentication mechanisms using (JWT) to protect user sessions and ensure security of API endpoints
\item Utilized input validation, parameterized queries, and secure coding practices to prevent common web vulnerabilities such as SQL injection, XSS, and CSRF attacks.
\item\bf{Learnings }{: Flask api | web security | javascript }
\end{itemize}
\smallskip
\cvproject{DriveAlert :RealTime Drowsiness Detection System}
\begin{itemize}
\item Trained deep Learning model to give real-time alert sounds to reduce accidents and enhance driver safety.
\item Created a interactive web interface with user authorization using Flask. Added Yawning detection \& integrated with cctv cameras.
\item\bf{Learnings }{: Flask | Web Security | ML Algorithm}
\end{itemize}
\smallskip
\cvproject{{Blood Donation Management \& Scheduling App}}
\begin{itemize}
\item Designed a secure system architecture implementing secure communication protocols with user authentication and access control.
\item Employed best practices in cybersecurity to safeguard sensitive donor and recipient information.
\item\bf{Learnings }{: Java | Firebase |Android studio }
\end{itemize}



\cvsection{Responsibility}
\cvproject{{Volunteer, Sparkling Wing NGO || NSS cell}}
\begin{itemize}
    \item  \normalfont Led educational sessions for underprivileged students, fostering a supportive learning environment.
    \item Demonstrated leadership by organizing lesson plans and guiding group activities to enhance understanding and engagement.
\item Delivered presentations among diverse audiences, showcasing strong public speaking skills \& confidence.
\item \bf{NSS:}\normalfont{ Engaged in beach cleaning activities to promote environmental sustainability and community welfare with Environmental Awareness Campaign .}
\end{itemize}


